---
title: "Convert NaCRRI DCas20-5419 to VCF"
site: workflowr::wflow_site
date: "2020-October-7"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---


# Input Parameters
```{r, eval=F}
#' @dartvcfInput input name and path of "vcf" file from DArT
#' @dartcountsInput input name and path of counts file from DArT
#' @outName output path and name
#' @nskipvcf number of "VCF" rows to skip on read-in
#' @nskipcounts number of "counts file" rows to skip on read in
#' @ncores number of cores to use, could be VERY memory intensive
#' @dartVars chr vector, column names that _are not_ sample IDs in the read-counts file. I use this internally to assign the sampleIDs in the VCF file

library(tidyverse); library(magrittr)
dartvcfInput<-here::here("data/Report-DCas20-5419","Report_5419_VCF_Ref_Version6.txt")
dartcountsInput<-here::here("data/Report-DCas20-5419","Report_5419_Counts_Ref_Version6.csv")
outName<-here::here("data/Report-DCas20-5419","DCas20_5419")
nskipvcf<-2 
nskipcounts<-3
ncores<-10
```

# Prelim. check format

Start manual. Check that the files read in according to previous code. Adjust code if necessary. Make a function and apply it to the input files.

```{r, eval=F}
# vcf<-read.table(dartvcfInput,
#                 stringsAsFactors = F,skip = nskipvcf, header = T, sep = "\t", comment.char = "")
# readCounts<-read.csv(dartcountsInput, stringsAsFactors = F,header = T,skip=nskipcounts)
# 
# dim(vcf)
# # [1] 13603  2052
# dim(readCounts)
# # [1] 27206  2068
# 
# # the lenghts don't match?
# 
# # Initial look at names....
# colnames(readCounts)[1:100]
#  #  [1] "AlleleID"                      "CloneID"                      
#  #  [3] "AlleleSequence"                "TrimmedSequence"              
#  #  [5] "TrimmedSequence_plus_Strand"   "Chrom_Cassava_v61"            
#  #  [7] "Tag_ChromPos_Cassava_v61"      "SNP_ChromPos_Cassava_v61"     
#  #  [9] "AlnCnt_Cassava_v61"            "AlnEvalue_Cassava_v61"        
#  # [11] "Strand_Cassava_v61"            "SNP"                          
#  # [13] "SnpPosition"                   "CallRate"                     
#  # [15] "OneRatioRef"                   "OneRatioSnp"                  
#  # [17] "FreqHomRef"                    "FreqHomSnp"                   
#  # [19] "FreqHets"                      "PICRef"                       
#  # [21] "PICSnp"                        "AvgPIC"                       
#  # [23] "AvgCountRef"                   "AvgCountSnp"                  
#  # [25] "RepAvg"                        "GS_Prediction_NaCRRI_2019_2"  
#  # [27] "GS_Prediction_NaCRRI_2019_1"   "GS_Prediction_NaCRRI_2019_26" 
#  # [29] "GS_Prediction_NaCRRI_2019_28"  "GS_Prediction_NaCRRI_2019_64" 
#  # [31] "GS_Prediction_NaCRRI_2019_77"  "GS_Prediction_NaCRRI_2019_92" 
#  # [33] "GS_Prediction_NaCRRI_2019_80"  "GS_Prediction_NaCRRI_2019_3"  
#  # [35] "GS_Prediction_NaCRRI_2019_14"  "GS_Prediction_NaCRRI_2019_52"
# colnames(vcf)[1:30]
# #  [1] "X.CHROM"                      "POS"                         
# #  [3] "ID"                           "REF"                         
# #  [5] "ALT"                          "QUAL"                        
# #  [7] "FILTER"                       "INFO"                        
# #  [9] "FORMAT"                       "GS_Prediction_NaCRRI_2019_2" 
# # [11] "GS_Prediction_NaCRRI_2019_11" "GS_Prediction_NaCRRI_2019_12"
# # [13] "GS_Prediction_NaCRRI_2019_13" "GS_Prediction_NaCRRI_2019_3" 
# # [15] "GS_Prediction_NaCRRI_2019_4"  "GS_Prediction_NaCRRI_2019_5" 
# # [17] "GS_Prediction_NaCRRI_2019_6"  "GS_Prediction_NaCRRI_2019_7" 
# # [19] "GS_Prediction_NaCRRI_2019_8"  "GS_Prediction_NaCRRI_2019_9" 
# # [21] "GS_Prediction_NaCRRI_2019_10" "GS_Prediction_NaCRRI_2019_1" 
# # [23] "GS_Prediction_NaCRRI_2019_23" "GS_Prediction_NaCRRI_2019_24"
# # [25] "GS_Prediction_NaCRRI_2019_25" "GS_Prediction_NaCRRI_2019_14"
# # [27] "GS_Prediction_NaCRRI_2019_15" "GS_Prediction_NaCRRI_2019_17"
# # [29] "GS_Prediction_NaCRRI_2019_18" "GS_Prediction_NaCRRI_2019_19"

# Need to add a check in the conversion function 
# that matches the names and reorders if necessary...

#... turns out, the function already checks for that!!  
# But seriously... the two outputs should come in the same order to avoid downstream problems.

```

# Conversion function

Available and sourced from `code/` subdirectory: `convertDart2vcf.R`.

# Run conversion function
```{r, eval=F}
source(here::here("code/","convertDart2vcf.R"))
convertDart2vcf(dartvcfInput,dartcountsInput,outName,
                nskipvcf=2,nskipcounts=3,ncores)
```

# Genomewide to per-chrom VCFs

Split the genome-wide VCF into per-chromosome VCFs for imputation.

```{r,eval = FALSE}
require(furrr); options(mc.cores=18); plan(multiprocess)
source(here::here("code","imputationFunctions.R"))

vcfIn<-here::here("data/Report-DCas20-5419","DCas20_5419.vcf.gz")
filters<-"--minDP 4 --maxDP 50" # because using GT not PL for impute (Beagle5)
outPath<-here::here("data/Report-DCas20-5419/")
outSuffix<-"DCas20_5419"

future_map(1:18,
           ~splitVCFbyChr(Chr=.,
                          vcfIn=vcfIn,filters=filters,
                          outPath=outPath,outSuffix=outSuffix))
```

2043 clones, 12981 SNP
